From physical principles to ???

### 2016-05-12 2015CompleteDerivation/completeDerivation.tex
Including Christine comments on classical systems

We'll see that very similar relationships are what define Hamiltonian and Lagrangian mechanics. But recovering them in the continuous case is trickier, and in fact will be part of the challenge in the following sections. Consider the map $q'=aq$ with $0<a<1$. At first glance, it's a bijective continuous map so we may think it can represent a deterministic and reversible evolution. Yet, $\Delta q \equiv [-b, b] \supset \Delta q'$: a set of states is mapped to a proper subset (i.e. to fewer states) which does not make sense for a reversible process. In the limit where we apply the map an infinite amount of times, any value of $q$ will be brought infinitely close to $0$, which also does not sound like a reversible process. The issue is that while deterministic evolution will map points to points, not all point to point maps can be considered deterministic and reversible. Discrete sets already come with a way to measure and compare the number of elements which is preserved by any bijective map. With continuous sets, we need to do extra work to properly define a measure (or metric) that allows to count states and possibilities.

@@

\subsection{Homogeneous decomposable systems}
The notion that a system is decomposable means the states are equipped with a rule of composition that allows one to write $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$: the composite system is the sum of its parts. For example, the state of a ball is equal to the state of its left and right parts.

The notion that the system is homogeneous means that the states of the composite and of the parts are not unrelated: they are made of the same material.\footnote{Whether a system is homogeneous depends on context (e.g. air can be thought as homogeneous if the mixture of gases does not change in space or in time due to phase transitions or chemical processes) and one must check that such property is maintained by time evolution.} In fact, the state space $\mathcal{C}$ of all systems composed of such material will include the state of the system as well as the states of all its parts (i.e. $\mathcal{c}, \mathcal{c}_1, \mathcal{c}_2 \in \mathcal{C}$). Since combining any two systems made of a homogeneous material will always give us a system made of the same homogeneous material (e.g. combining elements made of water gives us another element made of water), the state space $\mathcal{C}$ is closed under composition.

@@

\subsection{Classical homogeneous systems}
We also want to be able to express the state of the composite system in terms of the state of the parts. For example, given the state of a fluid we'll want to know how the material is distributed in space. This in general will depend on how much the state of the composite system "knows" about its parts. For example, the position and orientation of an ideal rigid body is enough to define where all its constituents are, while the volume/pressure/temperature of an ideal gas is not enough to determine the position and momentum of all its molecules. Therefore we need to characterize the system further.

We will call a classical system one that is infinitesimally reducible. That is: it is made of arbitrarily small parts, which we call particles, and the state of the whole system coincides with the sum of the states of the parts. Given the state space $\mathcal{S}$ for the infinitesimal parts, which we assume it to be a manifold consistently with \ref{continuous_state_space}, a composite state $\mathcal{c}$ will tell us the amount of material for each possible particle state. That is, each state is fully identified by a function $\rho: \mathcal{S} \to \mathbbm{R}$ that returns the amount of material in the composite state $\mathcal{c}$ that is prepared in the particle state $\mathcal{s}$. For example, given a certain configuration of gas, we can tell the density of material that is at a specific point in space with a specific value of momentum.

The notion that the parts are infinitesimal requires the co-domain of $\rho$ to be a real number, as opposed to an integer. The state space $\mathcal{S}$, instead, can have a discrete topology. For example, for a system composed of different tanks connected by pipes, the state of the composite system could be the overall distribution of water among the tanks. The amount in each tank is continuous (as we assume the water to be infinitesimally divisible) yet there are only a finite number of tanks the water can be placed into. As it links two physically distinguishable objects, $\rho$ is a continuous function as discussed before.

As we combine the states of different parts, we sum the distributions over particle states $\rho(\mathcal{s})=\rho_1(\mathcal{s})+\rho_2(\mathcal{s})$: the amount of material in the composite state is the sum of the amount of material of the parts. We can also increase or decrease the amount of material by a constant factor $\rho_1(\mathcal{s})=a\rho_2(\mathcal{s})$. This gives us the structure of a real vector space that is isomorphic to a subspace of continuous functions.

@@

Consider the set of transformations $T$ that increase or decrease the amount of material in the system by a constant factor. We claim $T$ is a field\footnote{Here field is intended in the abstract algebraic sense (a nonzero commutative division ring) which has no relationship to the field in the physics or differential geometry sense (a physical quantity/tensor with a value for each point in space).} isomorphic to $\mathbbm{R}$. Consider $\tau: \mathbbm{R} \rightarrow T$ the mapping between a number and the transformation that increases or decreases the amount of material by that number. This transformation exists: the system is infinitesimally decomposable and the amount can be changed continuously. Define on $T$ an addition $+: T \times T \rightarrow T$ and a multiplication $*: T \times T \rightarrow T$ such that $\tau(a) + \tau(b) = \tau(a+b)$ and $\tau(a) * \tau(b) = \tau(a*b)$, $a,b \in \mathbbm{R}$, so that the sum and product of the transformation is equal to the sum and product of their respective factors. $\tau$ is an isomorphism between $T$ and $\mathbbm{R}$ as fields.

@@

We claim $\mathcal{C}$ is isomorphic to a subspace of $C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. $\forall \mathcal{c} \in \mathcal{C} \exists ! \rho_{\mathcal{c}}:\mathcal{S} \rightarrow \mathbbm{R}$ returning the amount of material for each state $\mathcal{s} \in \mathcal{S}$. $\rho_{\mathcal{c}} \in C(\mathcal{S})$ by \ref{continuous_map}. Let $\varrho : \mathcal{C} \rightarrow C(\mathcal{S})$ such that $\varrho(\mathcal{c}) \mapsto \rho_\mathcal{c}$. 
As the system is reducible, two distinct composite states must represent different distributions. $\forall \mathcal{c_1}, \mathcal{c_2} \in \mathcal{C}, \mathcal{c_1} \neq \mathcal{c_2} \implies \varrho(\mathcal{c_1}) \neq \varrho(\mathcal{c_1})$. $\varrho$ is injective. $\varrho$ is a bijection between $\mathcal{C}$ and $\varrho(\mathcal{C})$. Let $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$, then $\varrho(\mathcal{c})=\varrho(\mathcal{c}_1)+\varrho(\mathcal{c}_2)$ as the amount of material of the composition of two states is the sum of the individual amounts. Let $\mathcal{c}_1=\tau(a)\mathcal{c}_2$, then $\varrho(\mathcal{c}_1)=a \varrho(\mathcal{c}_2)$ as $\tau(a)$ increases the amount of material by the factor $a$. $\varrho$ is a homomorphism. $\mathcal{C}$ is isomorphic to $\varrho(\mathcal{C}) \subseteq C(\mathcal{S})$ as vector spaces.
\end{justification}

@@

The ability to associate finite amount of material with sets of states allows us to define finite regions of $\mathcal{S}$ and compare them. Consider a region of position and momentum in phase space. If we are able to spread a finite amount of material into a non-infinitesimal uniform distribution, then we know we have a finite region. And the density will give us an indication of how big the region is: if we double the region, the density will halve. In other words: because we are describing densities over $\mathcal{S}$, we are able to give a unique measure $\mu$ for the size of sets of $\mathcal{S}$. From the measure we get a metric $d\mu$ and our positive linear functionals become integrals: $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$.

@@

\begin{justification}
	We claim there exists a positive linear functional $\Lambda_U : \mathcal{C} \rightarrow \mathbbm{R}$ for each $U \subseteq \mathcal{S}$ for which $\Lambda_U = \Lambda_{\mathrm{int}(U)}$. Let $\Lambda_{U} : \mathcal{C} \rightarrow \mathbbm{R}$ be the functional that returns the amount of material in $\mathcal{c}$ compatible with the outcome associated with the open set $U \subseteq \mathcal{S}$. $\Lambda_U$ is linear. $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$ as it has to be consistent with the operations of composing states and increasing/decrease the amount of material by a factor. $\Lambda_U$ is positive. If the value of the distribution for each particle state is positive then the total amount of material is positive. Let $U \subseteq \mathcal{S}$ not necessarily open. Define $\Lambda_U$ as $\Lambda_{\mathrm{int}(U)}$.

	We claim that $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$. Let $U \subseteq \mathcal{S}$ be an open set of particle states associated with an outcome. Let $\mathcal{c} \in \mathcal{S}$ a composite state. The amount of material of $\mathcal{c}$ associated with the outcome $U$ must be finite, as physically we always work with finite quantities. $|\Lambda_{U}(\mathcal{c})| < \infty$. Let $U \subseteq \mathcal{S}$ not necessarily open. The same argument applies to $\mathrm{int}(U)$.

@@

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$.  Each $\mathcal{s} \in \mathcal{S}$ is identified by a finite number of independent state variables. $\mathcal{S}$ is a manifold. $\mathcal{S}$ is locally compact. $\mathcal{C} \cong G \subseteq C(\mathcal{S})$ therefore $\Lambda_U(\mathcal{c}) \cong \Lambda_U(\rho_\mathcal{c})$. $\Lambda = \{\Lambda_U : C(\mathcal{S}) \rightarrow \mathbbm{R}\}_{U \subseteq \mathcal{S}}$ is a family of positive linear functionals such that $\forall U \subseteq \mathcal{S} \; \Lambda_U = \Lambda_{\mathrm{int}(U)}$ and $\Lambda_{U_1} + \Lambda_{U_2} = \Lambda_{U_1 \cup U_2} + \Lambda_{U_1 \cap U_2} \; \forall U_1, U_2 \subseteq \mathcal{S}$. For the extension \ref{extended_riesz_theorem} of the Riesz representation theorem for linear functionals 
	there exists a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_{U} \rho_\mathcal{c} d\mu$.

	We claim $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$. As per \ref{classical_vector space} $\mathcal{C}$, is isomorphic to a subspace $G \subseteq C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. As $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$, then $G \subseteq \{ \rho : S \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq S\} = L^1(\mathcal{S}, \mu)$ for \ref{everywhere_integrable_is_lebesgue_integrable}.  $G \subseteq C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$. Let $\rho_\mathcal{c}$ be the distribution associated with the state $\mathcal{c}$. Let $\rho \in C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ be a continuous function everywhere integral. If $\rho_\mathcal{c} \neq \rho$ then $\exists U \in \mathcal{S} | \int_{U} \rho_\mathcal{c} d \mu \neq \int_{U} \rho d \mu$. There exist an outcome in $\mathcal{S}$ that can physically distinguish the two distributions. There must be a state $\mathcal{c}_1 \in \mathcal{C} \; | \; \varrho_(\mathcal{c}_1)=\rho$. $\varrho : \mathcal{C} \rightarrow C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ is surjective. $\varrho$ is an isomorphism between $\mathcal{C}$ and $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as vector spaces.
\end{justification}

As we identified $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as the set of distributions that are physically meaningful, it's useful to briefly show how other commonly used functions spaces do not fit the bill. The set of continuous functions $C(\mathcal{S})$ would include functions that diverge at infinity. The set of continuous functions with compact support $C_C(\mathcal{S})$ would exclude Gaussians. The set of continuous functions that vanish at infinity $C_0(\mathcal{S})$ includes function whose integral is infinite. Schwartz space $S(\mathcal{S})$ excludes functions that are not infinitely smooth which we don't have a physical argument for. The set of Lebesgue integrable functions $L^1(\mathcal{S})$ includes discontinuous functions that for \ref{continuous_map} are unphysical.

@@

We now turn our attention to the metric $d\mu$ which we need to properly identify. It turns out that before we can do it, we need to better characterize $\mathcal{S}$.

>>>>

We'll see that very similar relationships are what define Hamiltonian and Lagrangian mechanics. But recovering them in the continuous case is trickier, and in fact will be part of the challenge in the following sections. Consider the map $q'=aq$ with $0<a<1$. At first glance, it's a bijective continuous map so we may think it can represent a deterministic and reversible evolution. Yet, $\Delta q \equiv [-b, b] \supset \Delta q'$: a set of states is mapped to a proper subset (i.e. to fewer states) which does not make sense for a reversible process. In the limit where we apply the map an infinite amount of times, any value of $q$ will be brought infinitely close to $0$, which also does not sound like a reversible process. The issue is that while deterministic evolution will map points to points, not all point to point maps can be considered deterministic and reversible. Discrete sets already come with a way to measure and compare the number of elements which is preserved by any bijective map. With continuous sets, we need to do extra work to properly define a measure (or metric) that allows one to count states and possibilities.

@@

\subsection{Homogeneous decomposable systems}
The notion that a system is decomposable means the states are equipped with a rule of composition that allows one to write $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$: the composite system is the sum of its parts. For example, the state of a ball is equal to the state of its top and bottom parts.

The notion that the system is homogeneous means that the states of the composite and of the parts are not unrelated: they are made of the same material.\footnote{Whether a system is homogeneous depends on context (e.g. air can be thought as homogeneous if the mixture of gases does not change in space or in time due to phase transitions or chemical processes) and one must check that such property is maintained by time evolution.} In fact, the state space $\mathcal{C}$ of all systems composed of such material will include the state of the system as well as the states of  its parts (i.e. $\mathcal{c}, \mathcal{c}_1, \mathcal{c}_2 \in \mathcal{C}$). Since combining any two systems made of a homogeneous material will always give us a system made of the same homogeneous material (e.g. combining elements made of water gives us another element made of water), the state space $\mathcal{C}$ is closed under composition.

@@

\subsection{Classical homogeneous decomposable systems}
We also want to be able to express the state of the composite system in terms of the state of each part. For example, given the state of a fluid we'll want to know how the material is distributed in space. This in general will depend on how much the state of the composite system "knows" about its parts. For example, the position and orientation of an ideal rigid body is enough to define where all its constituents are, while the volume/pressure/temperature of an ideal gas is not enough to determine the position and momentum of all its molecules. Therefore we need to characterize the system further.

We will call a classical system one that is infinitesimally reducible. That is, it is made of arbitrarily small parts, which we call particles, and giving the state of the whole system is equivalent to giving the states of all parts. Given the state space $\mathcal{S}$ for the infinitesimal parts, which we assume to be a manifold consistently with \ref{continuous_state_space}, a composite state $\mathcal{c} \in \mathcal{C}$ will tell us the amount of material for each possible particle state. That is, each state is fully identified by a function $\rho_\mathcal{c}: \mathcal{S} \to \mathbbm{R}$ that returns the amount of material in the composite state $\mathcal{c}$ that is prepared in the particle state $\mathcal{s}$. For example, given a certain configuration of gas, we can tell the density of material that is at a specific point in space with a specific value of momentum.

The notion that the parts are infinitesimal requires the co-domain of $\rho_\mathcal{c}$ to be a real number, as opposed to an integer. The state space $\mathcal{S}$, instead, can have a discrete topology. For example, for a system composed of different tanks connected by pipes, the state of the composite system could be the overall distribution of water among the tanks. The amount in each tank is continuous (as we assume the water to be infinitesimally divisible) yet there are only a finite number of tanks the water can be placed into. As it links two physically distinguishable objects, $\rho_\mathcal{c}$ is a continuous function as discussed before.

As we combine the states of different parts, we sum the distributions over particle states $\rho_{\mathcal{c}}(\mathcal{s})=\rho_{\mathcal{c}_1}(\mathcal{s})+\rho_{\mathcal{c}_2}(\mathcal{s})$: the amount of material in the composite state is the sum of the amount of material of the parts. We can also increase or decrease the amount of material by a constant factor $\rho_{\mathcal{c}_1}(\mathcal{s})=a\rho_{\mathcal{c}_2}(\mathcal{s})$. This gives us the structure of a real vector space that is isomorphic to a subspace of continuous functions.

@@

Consider the set of transformations $T$ that increase or decrease the amount of material in the system by a constant factor. We claim $T$ is a field\footnote{Here field is intended in the abstract algebraic sense (a nonzero commutative division ring) which has no relationship to the field in the physics or differential geometry sense (a physical quantity/tensor with a value for each point in space).} isomorphic to $\mathbbm{R}$. Consider $\tau: \mathbbm{R} \rightarrow T$ the mapping between a number and the transformation that increases or decreases the amount of material by that factor. This transformation exists: the system is infinitesimally decomposable and the amount can be changed continuously. Define on $T$ an addition $+: T \times T \rightarrow T$ and a multiplication $*: T \times T \rightarrow T$ such that $\tau(a) + \tau(b) = \tau(a+b)$ and $\tau(a) * \tau(b) = \tau(a*b)$, $a,b \in \mathbbm{R}$, so that the sum and product of the transformation is equal to the sum and product of their respective factors. $\tau$ is an isomorphism between $T$ and $\mathbbm{R}$ as fields.

@@

We claim $\mathcal{C}$ is isomorphic to a subspace of $C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. $\forall \mathcal{c} \in \mathcal{C} \exists ! \rho_{\mathcal{c}}:\mathcal{S} \rightarrow \mathbbm{R}$ returning the amount of material for each state $\mathcal{s} \in \mathcal{S}$. $\rho_{\mathcal{c}} \in C(\mathcal{S})$ by \ref{continuous_map}. Let $\varrho : \mathcal{C} \rightarrow C(\mathcal{S})$ such that $\varrho(\mathcal{c}) \mapsto \rho_\mathcal{c}$. 
As the system is reducible, two distinct composite states must represent different distributions. $\forall \mathcal{c_1}, \mathcal{c_2} \in \mathcal{C}, \mathcal{c_1} \neq \mathcal{c_2} \implies \varrho(\mathcal{c_1}) \neq \varrho(\mathcal{c_2})$. $\varrho$ is injective. $\varrho$ is a bijection between $\mathcal{C}$ and $\varrho(\mathcal{C})$. Let $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$, then $\varrho(\mathcal{c})=\varrho(\mathcal{c}_1)+\varrho(\mathcal{c}_2)$ as the amount of material of the composition of two states is the sum of the individual amounts. Let $\mathcal{c}_1=\tau(a)\mathcal{c}_2$, then $\varrho(\mathcal{c}_1)=a \varrho(\mathcal{c}_2)$ as $\tau(a)$ increases the amount of material by the factor $a$. $\varrho$ is a homomorphism. $\mathcal{C}$ is isomorphic to $\varrho(\mathcal{C}) \subseteq C(\mathcal{S})$ as a vector space.
\end{justification}

@@

The ability to associate finite amount of material with sets of states allows us to define finite regions of $\mathcal{S}$ and compare them. Consider a region of position and momentum in phase space. If we are able to spread a finite amount of material into a non-infinitesimal uniform distribution, then we know we have a finite region. And the density will give us an indication of how big the region is: if we double the region, the density will halve. In other words: because we are describing densities over $\mathcal{S}$, we are able to give a unique measure $\mu$ for the size of sets of $\mathcal{S}$. From the measure we get a metric $d\mu$ and our positive linear functionals become integrals, $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$.

@@

\begin{justification}
	We claim there exists a positive linear functional $\Lambda_U : \mathcal{C} \rightarrow \mathbbm{R}$ for each $U \subseteq \mathcal{S}$ such that $\Lambda_U = \Lambda_{\mathrm{int}(U)}$. Let $\Lambda_{U} : \mathcal{C} \rightarrow \mathbbm{R}$ be the functional that returns the amount of material in $\mathcal{c}$ compatible with the outcome associated with the open set $U \subseteq \mathcal{S}$. $\Lambda_U$ is linear. $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$ as it has to be consistent with the operations of composing states and increasing/decreasing the amount of material by a factor. $\Lambda_U$ is positive. If the value of the distribution for each particle state is positive then the total amount of material is positive. Let $U \subseteq \mathcal{S}$ not necessarily open. Define $\Lambda_U$ as $\Lambda_{\mathrm{int}(U)}$.

	We claim that $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$. Let $U \subseteq \mathcal{S}$ be an open set of particle states associated with an outcome. Let $\mathcal{c} \in \mathcal{C}$ a composite state. The amount of material of $\mathcal{c}$ associated with the outcome $U$ must be finite, as physically we always work with finite quantities. $|\Lambda_{U}(\mathcal{c})| < \infty$. Let $U \subseteq \mathcal{S}$ not necessarily open. The same argument applies to $\mathrm{int}(U)$.

@@

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$.  Each $\mathcal{s} \in \mathcal{S}$ is identified by a finite number of independent state variables. $\mathcal{S}$ is a manifold. $\mathcal{S}$ is locally compact. $\mathcal{C} \cong G \subseteq C(\mathcal{S})$ therefore $\Lambda_U(\mathcal{c}) \cong \Lambda_U(\rho_\mathcal{c})$. $\Lambda = \{\Lambda_U : C(\mathcal{S}) \rightarrow \mathbbm{R}\}_{U \subseteq \mathcal{S}}$ is a family of positive linear functionals such that $\forall U \subseteq \mathcal{S} \; \Lambda_U = \Lambda_{\mathrm{int}(U)}$ and $\Lambda_{U_1} + \Lambda_{U_2} = \Lambda_{U_1 \cup U_2} + \Lambda_{U_1 \cap U_2} \; \forall U_1, U_2 \subseteq \mathcal{S}$. By the extension \ref{extended_riesz_theorem} of the Riesz representation theorem for linear functionals 
	there exists a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_{U} \rho_\mathcal{c} d\mu$.

	We claim $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$. As per \ref{classical_vector space}, $\mathcal{C}$ is isomorphic to a subspace $G \subseteq C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. As $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$, then $G \subseteq \{ \rho : S \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq S\} = L^1(\mathcal{S}, \mu)$ by \ref{everywhere_integrable_is_lebesgue_integrable}.  $G \subseteq C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$. Let $\rho_\mathcal{c}$ be the distribution associated with the state $\mathcal{c}$. Let $\rho \in C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ be a Lebesgue integrable continuous function. If $\rho_\mathcal{c} \neq \rho$ then $\exists U \in \mathcal{S} \; | \; \int_{U} \rho_\mathcal{c} d \mu \neq \int_{U} \rho d \mu$. There exists an outcome in $\mathcal{S}$ that can physically distinguish the two distributions. There must be a state $\mathcal{c}_1 \in \mathcal{C} \; | \; \varrho(\mathcal{c}_1)=\rho$. $\varrho : \mathcal{C} \rightarrow C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ is surjective. $\varrho$ is an isomorphism between $\mathcal{C}$ and $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as vector spaces.
\end{justification}

As we identified the set of Lebesque integrable continuous functions $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as the set of distributions that are physically meaningful, it's useful to briefly show how other commonly used function spaces do not fit the bill. The set of continuous functions $C(\mathcal{S})$ would include functions that diverge at infinity. The set of continuous functions with compact support $C_C(\mathcal{S})$ would exclude Gaussians. The set of continuous functions that vanish at infinity $C_0(\mathcal{S})$ includes functions whose integral is infinite. Schwartz space $S(\mathcal{S})$ excludes functions that are not infinitely smooth which we don't have a physical argument for. The set of Lebesgue integrable functions $L^1(\mathcal{S})$ includes discontinuous functions that for \ref{continuous_map} are unphysical.

@@

We now turn our attention to the metric $d\mu$ which we need to properly identify. It turns out that before we can do so, we need to better characterize $\mathcal{S}$.
